\documentclass[UTF8]{article}
\usepackage{enumerate}
\usepackage[hmargin=1in,vmargin=1in]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{url}
\usepackage{etaremune}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[dvipsnames]{xcolor}
\usepackage{sectsty}
\usepackage[dvipsnames]{xcolor}


\hypersetup{
  colorlinks,
  linkcolor={red!50!black},
  citecolor={blue!50!black},
  urlcolor={SeaGreen!90!black}}


\pagestyle{fancy}
\fancyhf{}
\lhead{Arpit Arora}
\chead{Publications}
\rhead{\thepage}
\thispagestyle{empty}
%sectionfont{\color{}}

\fancyfoot[C]{\textit{Last updated: \today}}

\begin{document}
\begin{center}
\indent \textbf{\LARGE Arpit Arora -- Publications} \\
\indent \rule{17cm}{0.4pt}\\
\end{center}

% \section*{Arpit Arora Publications}
\noindent \href{https://orcid.org/0000-0002-8354-7356}{ORCID},
\href{https://scholar.google.com/citations?hl=en&view_op=list_works&gmla=AOV7GLNCPW8IsoVHZWL3Sumnh4dkvyrQEiY_I89IFD-VGtxXg0TP0jjxWp8nf4Htfz_1LwikT9G49boR3z5UuLgICZawXMdc3K20R_rtOo8&user=imlwFcsAAAAJ}{Google Scholar}, \href{https://ui.adsabs.harvard.edu/search/q=docs(library%2FFoo0PCcyQRuwOWcZNDtIlw)&sort=date%20desc%2C%20bibcode%20desc&p_=0}{ADS}\\
refereed: 6 -- first author: 4 (1 in prep.)  -- citations : 108 (as of \today)
\section*{First author}
\begin{etaremune}

\item  \textbf{Arora, A.}, Chakrabarti, S., Sanderson, R. E. Accelerating the search: Unveiling dark matter through galactic acceleration. (In prep, submission expected end of Dec 2023.)

\item \textbf{Arora, A.}, Garavito-Camargo, N., Sanderson, R. E., Cunningham, E. C., Wetzel, A., Panithanpaisal, N., Barry, M. 2023. LMC-driven anisotropic boosts in stream--subhalo interactions. \textit{The Astrophysical Journal submitted}, arXiv:2309.15998. 


\item \textbf{Arora, A.}, Sanderson, R.E., Panithanpaisal, N., Cunningham, E.C., Wetzel, A. and Garavito-Camargo, N., 2022. On the stability of tidal streams in action space. \textit{The Astrophysical Journal}, 939(1), p.2. 
  
\item \textbf{Arora, A.} and Williams, L.L., 2020. Power-law Pseudo-phase-space Density Profiles of Dark Matter Halos: A Fluke of Physics?. \textit{The Astrophysical Journal}, 893(1), p.53. 
\end{etaremune}

\section*{N$^{th}$ author}
\begin{etaremune}

\item Ansar, S., Pearson, S., Sanderson, R. E., \textbf{Arora, A.}, Hopkins, P. F., Wetzel, A., Cunningham, E. C., Quinn, J. 2023. Bar formation and destruction in the FIRE-2 simulations. \textit{The Astrophysical Journal submitted}, arXiv:2309.16811.

\item Donlon, T., Newberg, H.J., Sanderson, R., Bregou, E., Horta, D., \textbf{Arora, A.} and Panithanpaisal, N.J., 2023. The Debris of the ``Last Major Merger'' is Dynamically Young. \textit{Monthly Notices of the Royal Astronomical Society submitted}, arXiv:2310.09376. 

\item Horta, D., Cunningham, E.C., Sanderson, R., Johnston, K.V., Deason, A., Wetzel, A., McCluskey, F., Garavito-Camargo, N., Necib, L., Faucher-Giguère, C.A., \textbf{Arora, A.} and Gandhi, P.J., 2023. The proto-galaxy of Milky Way-mass haloes in the FIRE simulations. \textit{Monthly Notices of the Royal Astronomical Society submitted}, arXiv:2307.15741. 

\item Garavito-Camargo, N., Price-Whelan, A.M.,  Cunningham, E.C., Samuel, J., Patel, E., Wetzel, A., Johnston, K.V., \textbf{Arora, A.}, Sanderson, R. and Garrison, L., 2023. LMC-mass satellite galaxies inducing ‘apparent’ co-rotation motions in Milky Way-like galaxies in
FIRE. \textit{The Astrophysical Journal submitted}.

\item Barry, M., Wetzel, A., Chapman, S., Samuel, J., Sanderson, R. and \textbf{Arora, A.}, 2023. The dark side of FIRE: predicting the population of dark matter subhaloes around Milky Way-mass galaxies. \textit{Monthly Notices of the Royal Astronomical Society}, 523(1), pp.428-440. 

\item Wetzel, A., Hayward, C.C., Sanderson, R.E., Ma, X., Anglés-Alcázar, D., Feldmann, R., Chan, T.K., El-Badry, K., Wheeler, C., Garrison-Kimmel, S., Nikakhtar, F., Panithanpaisal, N., \textbf{Arora, A.}, Gurvich, A.B., Samuel, J., Sameie, O., Pandya, V., Hafen, Z., Hummels, C., Loebman, S., Boylan-Kolchin, M., Bullock, J.S., Faucher-Giguere, C.-A., Keres, D. and Hopkins, P.F, 2023. Public data release of the FIRE-2 cosmological zoom-in simulations of galaxy formation. \textit{The Astrophysical Journal Supplement Series}, 265(2), p.44.


\item Horta, D., Cunningham, E.C., Sanderson, R.E., Johnston, K.V., Panithanpaisal, N., \textbf{Arora, A.}, Necib, L., Wetzel, A., Bailin, J. and Faucher-Giguère, C.A., 2023. The Observable Properties of Galaxy Accretion Events in Milky Way–like Galaxies in the FIRE-2 Cosmological Simulations. \textit{The Astrophysical Journal}, 943(2), p.158

\item Baptista, J., Sanderson, R., Huber, D., Wetzel, A., Sameie, O., Boylan-Kolchin, M., Bailin, J., Hopkins, P.F., Faucher-Giguere, C.A., Chakrabarti, S. and Vargya, D., Panithanpaisal, N., \textbf{Arora, A.} and Cunningham, E., 2022. Orientations of DM Halos in FIRE-2 Milky Way-mass Galaxies. \textit{The Astrophysical Journal}, 958(1), p.44.

\item Panithanpaisal, N., Sanderson, R.E., \textbf{Arora, A.}, Cunningham, E.C. and Baptista, J., 2022. Constraining the Tilt of the Milky Way's Dark Matter Halo with the Sagittarius Stream. \textit{The Astrophysical Journal in revision},  arXiv:2210.14983.


\end{etaremune}
\end{document}